A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-19 doc/paper1-submission/paper5.tex
Update.

>>>>

\subsubsection{Comparison to other supertree methods}

So, we also consider MRP and MinCut.  MRP can display edges not found
in any input tree, and so fails criterion #1.  MRP is used in many
studies that attempt to infer the true tree from a lot of input
trees.  To some extent, MRP tries to treat each tree as data, which
differs from our approach here.

MinCut (and Modified MinCut) attempts to favor relationships present
in multiple input trees during conflict resolution.

Both MRP and MinCut attempt to adjudicate conflicts in a way that
favors relationships present in more input trees.  Thus, they perform
something more like a weighted average.  However, the reason the
supertree resolves conflicts in a particular way is not clear and
transparent, and does not allow a method for curators to adjust the
supertree.

A number of other supertree methods exist, including Matrix
Representation with Parsimony (MRP) and MinCut.  MRP
% http://currents.plos.org/treeoflife/article/reweaving-the-tapestry-a-supertree-of-birds/
MRP - displays unsupported groups (#1), not rank-based (#2), ?
SuperFine - computes a strict consensus, then MRP
Minimum Flip - 
(Modified) MinCut -
